---
title: PORTFOLIO 1
output: html_document

---

#Project 1: Bellebeat


```{r}
library(tidyverse)
```

```{r}
daily_fit<- read.csv("daily_fit.csv")
daily_fit%>%
  head()
```

#Ask
The business task is clear. We have to study the Dataset that contains the data of fitbit users in order to find a trend or trends that could be usefull to Bellabeat company (a high-tech manufacturer of health-focused products for women)


#Prepare
For doing so, we'll have to study a dataframe available on Kaggle. The data contains no name or any others personal information on users.


#Process
I think the data needs to be cleaned.  The columns names mix upper cases and lower cases, and they also need underscores to make them easier to read.

```{r}
daily_fit%>%
  rename_with(tolower)%>%
  rename(total_steps=totalsteps,total_distance=totaldistance,tracker_distance=trackerdistance,date=activitydate)%>%
  head()
  
```


#Analzsing the Data
First we will have an overview of the data.

```{r}
summary(daily_fit)
```

We will first see what is the average steps and the average distance covered by users

```{r}
daily_fit%>%
  summarize(mean_TotalSteps= mean(TotalSteps))

daily_fit%>%
  summarize(mean_TotalDistance=mean(TotalDistance))
```

On average users made 7638 steps and covered 5.48 km.

Median distance:

```{r}
daily_fit%>%
  summarize(median_totalDistance=median(TotalDistance))
```

Mean Calories

```{r}
daily_fit%>%
  summarize(mean_calories=mean(Calories))
```

Median calories

```{r}

daily_fit%>%
  summarize(median_Calories=median(Calories))
```



Mean of user than cover 

We will see how data that are contained on this dataset are correlated (on not!).
 * assupmtion: 
 
1) Steps and Calories are correlated.
2) Distance and calories are correlated
3) Light activity and sedentarity are correlated

                       1 Steps and Calories

```{r}
daily_fit%>%
  summarize(cor_totalsteps_calories=cor(TotalSteps, Calories))%>%
  drop_na()
```

With a correlation of 0.59 we could conclude that those variables are correlated.
It would interesting to see if the distance is more correlated to the calories than than steps.
                               
                       2 Dsitance and Calories

```{r}
daily_fit%>%
  summarize(cor_totaldistance_calories=cor(TotalDistance, Calories))%>%
  drop_na()
```

With a correlation of 0.64 we can conclude that de distance is more correlated to the calories than the steps.
It's possible that the steps counter of the app is not as precise as we need. It could be improve to better fit the distance.

                       3 Sedentarity and low activity
                       
```{r}
daily_fit%>%
  summarize(cor_sedentaryactivity_lightactivity=cor(LightActiveDistance, SedentaryMinutes))
```

Those variables a negatively correlated. 
On the other hand there are no tie between the high activity and the sedentarity

```{r}
daily_fit%>%
  summarize(cor_veryactivedistance_sedentaryactivedistance=cor(VeryActiveDistance, SedentaryActiveDistance))%>%
  drop_na()
```
                       
#Share

Now, we will see visualizations of our analyses.

                        Distance and calories

```{r message=FALSE, warning=FALSE}
install.packages("car") 
install.packages("carData")
library(car)
scatterplot(TotalDistance~Calories,data= daily_fit, xlab= "TotalDistance", ylab="Calories", regline= TRUE
            ,ellipse= FALSE, smooth= FALSE, gride= TRUE)
```

                            Sedentary and low activity

```{r warning=FALSE}
scatterplot(SedentaryMinutes~LightlyActiveMinutes,data= daily_fit, xlab="SendentaryMinutes" , ylab="LightlyActiveMinutes", regline= TRUE ,ellipse= FALSE, smooth= FALSE, gride= TRUE)
```


```{r}
ggplot(data=daily_fit)+
  geom_point(mapping = aes(x=TotalDistance, y=Calories))+
  geom_smooth(mapping = aes(x=TotalDistance, y=Calories))
```

